Contracts for Contracts

### 2023-06-03 paper/introduction.tex
ieee template 2333

Indeed, in recent years, we have seen a number of failures of smart contract
systems due to attacks utilizing vulnerable contract programs.
For example, in the famous DAO hack\note{cite}, the unauthorized attacker is
able transfer money by constructing recursive function calls with
the callback mechanism, causing a total lose of \$50 million.
The root cause of this attack is that the deployed contract does not
checks reentrancy defensively before performing critical actions.

@@

To prevent such attacks, the programmer needs to specify those critical
conditions. The execution is allowed when those conditions are met.
However, we observe that existing popular smart contract languages (e.g.
Solidity) do not provide \emph{rich, effective, convenient} means to specify
and enforce contract behaviors.
Simple first-order assertion primitives (e.g., @require@) are indeed available,
but they cannot effectively examine callable addresses or function values, which
are a common pattern used in smart contract programs.
Moreover, many of the critical condition in smart contracts are \emph{temporal}
-- the order of happened events matters.
For instance, to defense the DAO attack caused by reentrancy via
external functions, it requires to check that the function of interest cannot
be invoked \emph{before} the current call of the same function is finished.

@@

%Apart from the investigating effort to certify and verify smart contract
%programs, language designers are responsible to empower programmers with better
%linguistic solutions to secure smart contracts in the first place.
In this paper, we argue that \emph{behavioral software contracts}
\cite{DBLP:conf/tools/Meyer98a} should play a fundamental role in the
development of \emph{smart contract} programs.  Similar to smart contracts,
behavioral contracts is an agreement too. They specify the assumptions and
guarantees between software components. The specified assumptions and
guarantees will be monitored and reported when violated in languages with
behavioral contracts.

@@

\paragraph{}

@@

\subsubsection*{\textbf{Contributions}} This paper makes the following contributions:
\begin{itemize}
  \item We design \lang, an extension for Solidity that allows programmers to
        specify and enforce higher-order and temporal behaviors in smart contracts.
        We demonstrate \lang's use cases through extensive examples and
        implement \lang as a preprocessor for ordinary Solidity programs.
	\item We present the core formalization $\lambda_\lang$ for our proposed
	      extension, including its syntax, formal semantics, compilation, and
	      soundness.
  \item We examine a number of real-world attacks with \lang, showing that our
        approach is effective in improving safety and reliability of smart contract
        programs.
  \item We evaluate the overhead of \lang compared to manually implemented
        assertions and checks, showing that our approach does not introduce
        additional runtime overhead.
\end{itemize}
\lang is open-sourced and publicly available at \note{url}.

>>>>

Indeed, in recent years, we have seen a number of failures of smart contract
systems due to attacks utilizing vulnerable contract programs.
For example, in the famous DAO hack\note{cite}, the unauthorized attacker is
able transfer money by constructing recursive function calls with
the callback mechanism, causing a total lose of \textdollar50 million.
The root cause of this attack is that the deployed contract does not
checks reentrancy defensively before performing critical actions.

@@

To prevent such attacks, the programmer needs to specify those critical
conditions. The execution is allowed when those conditions are met.
However, we observe that existing popular smart contract languages (e.g.
Solidity) do not provide \emph{rich, effective, convenient} means to specify
and enforce contract behaviors.
Simple first-order assertion primitives (e.g., \code{require}) are indeed available,
but they cannot effectively examine callable addresses or function values, which
are a common pattern used in smart contract programs.
Moreover, many of the critical condition in smart contracts are \emph{temporal}
-- the order of happened events matters.
For instance, to defense the DAO attack caused by reentrancy via
external functions, it requires to check that the function of interest cannot
be invoked \emph{before} the current call of the same function is finished.

% encode temporal behavioral checks using ad-hoc lower-level value behaviors

@@

%Apart from the investigating effort to certify and verify smart contract
%programs, language designers are responsible to empower programmers with better
%linguistic solutions to secure smart contracts in the first place.
In this paper, we argue that \emph{behavioral software
contracts}~\cite{DBLP:conf/tools/Meyer98a} should play a fundamental role in
the
development of \emph{smart contract} programs.  Similar to smart contracts,
behavioral contracts is an agreement too. They specify the assumptions and
guarantees between software components. The specified assumptions and
guarantees will be monitored and reported when violated in languages with
behavioral contracts.

@@

\paragraph{hey}

@@

\subsubsection*{\textbf{Contributions}} This paper makes the following contributions:
\begin{itemize}
  \item We design \lang, an extension for Solidity that allows programmers to
        specify and enforce higher-order and temporal behaviors in smart contracts.
        We demonstrate \lang's use cases through extensive examples and
        implement \lang as a preprocessor for ordinary Solidity programs.
	\item We present the core formalization $\lambda_\lang$ for our proposed
	      extension, including its syntax, formal semantics, compilation, and
	      soundness.
  \item We examine a number of real-world attacks with \lang, showing that our
        approach is effective in improving safety and reliability of smart contract
        programs.
  \item We evaluate the overhead of \lang compared to manually implemented
        assertions and checks, showing that our approach does not introduce
        additional runtime overhead.
\end{itemize}

\lang is open-sourced and publicly available at \note{url}.
